Machine Learning Methods for Site-specific Input Management

### 2022-03-16 Codes/PrepareResults.rmd

## MB yield response to N

@@

# --- MB function to N --- #
vis_res_y <- ggplot(res_y_dt[variable=="Yield"]) +
  geom_line(aes(x=N, y=value, color=factor(group))) +
  geom_point(data= sub_dt, aes(x=opt_N, y=value)) +
  geom_segment(data = sub_dt, aes(x = N, xend=N, y = value, yend=-Inf), linetype = "dashed") +
  labs(y = "Yield (kg/ha)") +
  labs(x = "N (kg/ha)") +
  theme_dist +
  theme(legend.position = "none")

@@

## MB yield response and estimated yield response by BRF
+ true yield response curves for two sites within a field
+ points true yield evaluated at the N rate that was actually applied at the site
+ RF-estimated yield at all the potential experimental rates including the actual rate that was applied

@@

vis_pred_y_res <- 
  ggplot() +
    # --- true yield response curve --- #
    geom_line(
      data=vis_res_true, aes(x=N, y=yield, group=factor(unique_subplot_id))
    ) +
    # --- Predicted yield points --- #
    geom_point(
      data=vis_res_pred, aes(x=N, y=pred_y_BRF, group=factor(unique_subplot_id)), color="red"
    ) +
    geom_point(data = vis_res_true[aa_n==N], aes(x=aa_n, y= yield), color = 'blue') +
    geom_segment(data = vis_res_true[aa_n==N], aes(x = aa_n, xend=aa_n, y = yield, yend=-Inf), linetype = "dashed") +
    labs(y = "Yield (kg/ha)") +
    labs(x = "N (kg/ha)") +
    theme_dist +
    theme(legend.position = "none")
```

@@

## True Yields vs Predicted Yields by models

>>>>

## MB yield response to N
+ for comment 8
+ The figure illustrates how yield responds to N

@@

# --- MB function to N --- #
vis_MB_curve <- ggplot(res_y_dt[variable=="Yield"]) +
  geom_line(aes(x=N, y=value, group=factor(group))) +
  geom_point(data= sub_dt, aes(x=opt_N, y=value)) +
  geom_segment(data = sub_dt, aes(x = N, xend=N, y = value, yend=-Inf), linetype = "dashed") +
  labs(y = "Yield (kg/ha)") +
  labs(x = "N (kg/ha)") +
  theme_dist +
  theme(legend.position = "none")

@@

## MB yield response and estimated yield response by BRF
+ As a response to comment 6
+ The figure shows the true yield response function and predicted yields at five N experiment by BRF

@@

vis_MB_BRF_y <- 
  ggplot() +
    # --- true yield response curve --- #
    geom_line(
      data=vis_res_true, aes(x=N, y=yield, group=factor(unique_subplot_id))
    ) +
    # --- Predicted yield points --- #
    geom_point(
      data=vis_res_pred, aes(x=N, y=pred_y_BRF, group=factor(unique_subplot_id)), color="red"
    ) +
    geom_point(data = vis_res_true[aa_n==N], aes(x=aa_n, y= yield), color = 'blue') +
    geom_segment(data = vis_res_true[aa_n==N], aes(x = aa_n, xend=aa_n, y = yield, yend=-Inf), linetype = "dashed") +
    labs(y = "Yield (kg/ha)") +
    labs(x = "N (kg/ha)") +
    theme_dist +
    theme(legend.position = "none")
```

@@

## True Yields vs Predicted Yields by models
+ for comment 7
+ a figure plots true yields (without error, epsilon) against predicted yields by model (without CF of course) for a single simulation round with RMSE printed for each model.
